Generating Random Logic Programs Using Constraint Programming

### 2020-08-16 seminar_talk/talk.tex
Move changes from the conference talk to the seminar talk

\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
    \textcolor{predicate}{\mathrm{stress}}$}
  \centering
  \begin{tikzpicture}
    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
    \draw[-{Latex[length=2mm]}] (person) -- (stress);
    \draw[-{Latex[length=2mm]}] (person) -- (spont);
    \draw[-{Latex[length=2mm]}] (person) -- (smoke);

    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (person);
    \draw<3->[-{Latex[length=2mm]}] (person) edge[draw=red,bend left=15] (friend);

    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
  \end{tikzpicture}
\end{frame}

@@

\section{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item The model can generate (approximately) realistic instances of reasonable
    size
  \item The main performance bottleneck can be addressed by generating programs
    with a simpler structure
  \item Open questions and future work
    \begin{itemize}
    \item Can the model be used to ensure uniform sampling?
    \item What is the reason behind all algorithms behaving similarly?
    \item Why does independence have no effect on inference time?
    \item Can random program generation be useful in learning?
    \end{itemize}
  \end{itemize}
  \pause
  \begin{block}{The implementation of the model is available at}
    \url{https://github.com/dilkas/random-logic-programs}
  \end{block}
\end{frame}

>>>>

\begin{frame}{Predicate Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
    \textcolor{predicate}{\mathrm{stress}}$}
  \centering
  \begin{tikzpicture}
    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
    \node[draw,ellipse,right=of friend,onslide=<5-6>{pattern=north east lines,pattern color=constant}] (influences) {\textcolor{predicate}{influences}};
    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
    \node[draw,ellipse,below=of stress,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (spont) {\textcolor{predicate}{cancer\_spont}};
    \node[draw,ellipse,below=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (smoke) {\textcolor{predicate}{cancer\_smoke}};
    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
    \node[draw,ellipse,right=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (cancer) {\textcolor{predicate}{cancer}};
    \node[draw,ellipse,above=of cancer,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (smokes) {\textcolor{predicate}{smokes}};
    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
    \draw[-{Latex[length=2mm]}] (person) -- (stress);
    \draw[-{Latex[length=2mm]}] (person) -- (spont);
    \draw[-{Latex[length=2mm]}] (person) -- (smoke);

    \draw<4>[-{Latex[length=2mm]}] (person) edge[draw=red] (friend);
    \draw<4>[-{Latex[length=2mm]}] (stress) edge[draw=red] (friend);
    \draw<4>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (friend);
    \draw<4>[-{Latex[length=2mm]}] (spont) edge[draw=red] (friend);
    \draw<4>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=20] (friend);
    \draw<4>[-{Latex[length=2mm]}] (smoke) edge[draw=red,bend left=20] (friend);

    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (person);
    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (person);
    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (person);
    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=15] (person);

    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (stress);
    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (stress);
    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red,bend right=15] (stress);
    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red] (stress);
  \end{tikzpicture}
\end{frame}

@@

\section{Conclusions}

\begin{frame}{Conclusions and Future Work}
  \begin{itemize}
  \item The model can generate (approximately) realistic instances of reasonable
    size
  \item The main performance bottleneck can be addressed by generating programs
    with a simpler structure
  \item Open questions and future work
    \begin{itemize}
    \item Can the model be used to ensure uniform sampling?
    \item What is the reason behind all algorithms behaving similarly?
    \item Why does independence have no effect on inference time?
    \item Can random program generation be useful in learning?
    \end{itemize}
  \end{itemize}
  \begin{block}{The implementation of the model is available at}
    \url{https://github.com/dilkas/random-logic-programs}
  \end{block}
\end{frame}
